\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-03-18 paper/main.tex
Added comments in the paper

\sloppy Serveral important application domains (e.g., transportation,
medicine, etc.) use AI as part of their business processes. Deep
Learning~(DL) libraries, such as \jax, \torch{}, and \tf{}, provide
the building blocks for the AI components of these applications.
Unfortunately, as any piece of software, these libraries contain
bugs. An impressive number of techniques have been recently proposed
to find bugs in these
libraries~\cite{wei2022free,xie2022docter,deng2022fuzzing,pham2019cradle,guo2020audee,wang2020deep,gu2022muffin,deng2023large,liu2023nnsmith,liu2023neuri,shi2023acetest,deng2023largeedge},
however we observe that the evaluation of these techniques do
\emph{not} use a reference set of reproducible bugs to evaluate their
effectiveness. The lack of evaluation standards is an obstacle to the
fair comparison of techniques, hindering research progress.

@@

@@

\begin{enumerate}[leftmargin=0.5cm]
  \item Select an issue following the criteria defined in Section~\ref{sec:selection-criterion};
  \item Write file \CodeIn{requirements.txt} with the list of dependencies to reproduce the bug;
  \item Create a file showing the code that causes the bug (for documentation);
  \item Create a file with a \CodeIn{pytest} test case that passes if
    the code triggers the buggy behavior documented in the issue;
    %% A python file is created that contains the bug revealing code, along with a test (pytest) that passes upon successfully trigerring the buggy behavior.
  \item If the bug depends on a CUDA-specific build, write a
    Dockerfile to create a container including the needed CUDA-driver
    and the other artifacts mentioned above (e.g., test file and
    requirements);
    %% along with the requirements.txt file and the python
    %% script copied into it.
  \item Write a script that creates the virtual environment (either
    Python's \CodeIn{Conda Enviroment}~\cite{venv} or Docker container) and runs
    the test on it;
  \item Create a directory \CodeIn{<lib>/<bug-id>} containing all the
    artifacts mentioned above, where \CodeIn{lib} refers to the
    affected library and \CodeIn{bug-id} is a fresh identifier of the
    bug instance.
    %% All files are put into a single self-contained folder with the issue id in the name so that the tools exposed by the framework of our tool can find and execute the the bug reproduction script.
\end{enumerate}

@@

\subsubsection{Running FreeFuzz~\cite{wei2022free} on \tname.}

@@

We anticipate two major use cases for \tname: (1) \textbf{evaluation
  of testing techniques} and (2) \textbf{evaluation of repair
  techniques}. Dozens of API- and model-level testing techniques have
been proposed in the literature recently and it is imperative to
evaluate them using a standard benchmark. \tname\ provides such
benchmark. Considering repair, as testing techniques mature it becomes
important to identify candidate repairs that can be recommended to
developers when reporting issues in bug trackers. With \tname\ it is
possible to identify if the problem has been resolved.

>>>>

\sloppy Serveral important application domains (e.g., transportation,
medicine, etc.) use AI as part of their business processes. Deep
Learning~(DL) libraries, such as \jax, \torch{}, and \tf{}, provide
the building blocks for the AI components of these applications.
Unfortunately, as any piece of software, these libraries contain
bugs. An impressive number of techniques have been recently proposed
to find bugs in these
libraries~\cite{wei2022free,xie2022docter,deng2022fuzzing,pham2019cradle,guo2020audee,wang2020deep,gu2022muffin,deng2023large,liu2023nnsmith,liu2023neuri,shi2023acetest,deng2023largeedge},
however we observe that the evaluation of these techniques do
\emph{not} use a reference set of reproducible bugs to evaluate their
effectiveness. The lack of evaluation standards is an obstacle to the
fair comparison of techniques, hindering research progress.
\Fix{Clarify how the "evaluation set" used by the existing works is different from the "reference set" that we are proposing. Also, need more compelling reason/some sort of evaluation of other fuzzers
to complement the motivation}

@@

\Fix{Need to add what labels were used, which period we took the issues from,
how many issues we looked at, define "bug reports", mention how many bugs had 
been filtered with each criterion}

@@

\begin{enumerate}[leftmargin=0.5cm]
  \item Select an issue following the criteria defined in Section~\ref{sec:selection-criterion};
  \item Write file \CodeIn{requirements.txt} with the list of dependencies to reproduce the bug; \Fix{Clarify that the version of the library which was used to report the bug is also included in the requirements.txt file}
  \item Create a file showing the code that causes the bug (for documentation);
  \item Create a file with a \CodeIn{pytest} test case that passes if
    the code triggers the buggy behavior documented in the issue;
    %% A python file is created that contains the bug revealing code, along with a test (pytest) that passes upon successfully trigerring the buggy behavior.
  \item If the bug depends on a CUDA-specific build, write a
    Dockerfile to create a container including the needed CUDA-driver
    and the other artifacts mentioned above (e.g., test file and
    requirements);
    %% along with the requirements.txt file and the python
    %% script copied into it.
  \item Write a script that creates the virtual environment (either
    Python's \CodeIn{Conda Enviroment}~\cite{venv} or Docker container) and runs
    the test on it;
  \item Create a directory \CodeIn{<lib>/<bug-id>} containing all the
    artifacts mentioned above, where \CodeIn{lib} refers to the
    affected library and \CodeIn{bug-id} is a fresh identifier of the
    bug instance.
    %% All files are put into a single self-contained folder with the issue id in the name so that the tools exposed by the framework of our tool can find and execute the the bug reproduction script.
\end{enumerate}

@@

\Fix{What evaluation can be added to this section?}
\subsubsection{Running FreeFuzz~\cite{wei2022free} on \tname.}

@@

We anticipate two major use cases for \tname: (1) \textbf{evaluation
  of testing techniques} and (2) \textbf{evaluation of repair
  techniques}. Dozens of API- and model-level testing techniques have
been proposed in the literature recently and it is imperative to
evaluate them using a standard benchmark. \tname\ provides such
benchmark. Considering repair, as testing techniques mature it becomes
important to identify candidate repairs that can be recommended to
developers when reporting issues in bug trackers. With \tname\ it is
possible to identify if the problem has been resolved. 
\Fix{The concept of repairing has not been tied to any commands in the tool. Suggestions include
a way to recreate an enviroment with the bug fixed, or a way to check if the bug has been fixed in a new version of the library.}
